Using SMT engine to generate Symbolic Automata\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2017-03-30 2017-Xudong-SMT/OpenPNets-SMT.tex
Add references
More references added in .bib.
References have already been cited.
Add the subscript of hb in the page 23.

There are other dedicated platforms, e.g. for the analyses of 
programming languages, making use of external automatic theorem
provers (ATP), or even some automatic tactics from interactive theorem
provers (ITP), to perform symbolic reasonning, and for example to
discharge some subgoals in the proofs.
In a similar way, there are several ATPs/ITPs we could consider to use for
the result pruning and bisimulation checking in our algorithm, as an
alternative to Z3, such as CVC4~\cite{}, Coq~\cite{},
Isabelle~\cite{} or others. Z3 is
developed by Microsoft Research based on the satisfiability modulo
theories (SMT), mainly applied in extended static checking, test case
generation, and predicate abstraction. Tools like Isabelle and
Rodin have already integrated SMT solvers as modules for proving the
theorem or formula inputed by users.

>>>>

There are other dedicated platforms, e.g. for the analyses of 
programming languages, making use of external automatic theorem
provers (ATP), or even some automatic tactics from interactive theorem
provers (ITP), to perform symbolic reasonning, and for example to
discharge some subgoals in the proofs.
In a similar way, there are several ATPs/ITPs we could consider to use for
the result pruning and bisimulation checking in our algorithm, as an
alternative to Z3, such as CVC4~\cite{barrett:CAV2011}, Coq~\cite{armand:CPP2011,besson:CPP2011},
Isabelle~\cite{blanchette:FroCoS2011} or others. Z3 is
developed by Microsoft Research based on the satisfiability modulo
theories (SMT), mainly applied in extended static checking, test case
generation, and predicate abstraction. Tools like Isabelle and
Rodin~\cite{deharbe2013,deharbe2014,abrial2007} have already integrated SMT solvers as modules for proving the
theorem or formula inputed by users.
